Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)

### 2021-09-11 docs/manuscript/manuscript.tex
update: minor edits

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)},
  pdfauthor={Brad McKay1 \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Meta-science; GRIMMER; Effect sizes; Perceptual motor learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{xcolor}
\raggedbottom
\pagewiselinenumbers
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
\date{}

@@

We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015). All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. The five articles will be referred to throughout this paper using the following numbering system:

@@

The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2). In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (CSAI-2) (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale. Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.

@@

None of the five articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2 through 5 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2 through 5. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication that we were concerned about irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1 and provided some more general responses to our concerns; however, elements of their responses were inaccurate relative to the target articles. The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data \emph{and} analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: \textbf{{[}LINK{]}}.

@@

To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}). We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation. The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97. In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology literature. The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.

@@

\caption{Absolute Cohen's \(d\) estimates from Articles 1-4 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by light green and dark blue regions of the figure, reaching a maximum value of \(d\) = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the purple and dark blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
\end{figure}

@@

Eta-squared (\(\eta^{2}\)) is calculated by dividing the sum of squares for the effect by the total sum of squares. It can be interpreted as analogous to \(R^{2}\) as it represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an ANOVA (Lakens, 2013). Benchmarks have been suggested for small, medium, and large effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988). Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as we will see commonly below, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone. Such a result is implausible.

@@

We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015). These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A. Lola, personal communication, April 22, 2021). Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that their results and discussions remain valid despite these aforementioned typographic errors in the tables. Considering these findings, it seems the conclusions from these articles are not reliable.

It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations. Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021), possibly because the results appeared to be exemplary. Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication. We cannot rule out that these papers were selected for publication because of exemplary results and happened to have errors, and this selection caused those errors to correlate with the authors' expectations.

Other irregularities, such as a repeating \emph{F}-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation. Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed. These errors were pervasive and appear to have substantially affected the conclusions of the articles in question. At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process. Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-08-20), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.

@@

\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: \textbf{{[}LINK{]}}.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-anaya2016}{}%
Anaya, J. (2016). \emph{The GRIMMER test: A method for testing the validity of reported measures of variability}. \url{https://doi.org/10.7287/peerj.preprints.2400v1}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-bakker2011}{}%
Bakker, M., \& Wicherts, J. M. (2011). The (mis)reporting of statistical results in psychology journals. \emph{Behavior Research Methods}, \emph{43}(3), 666--678. \url{https://doi.org/10.3758/s13428-011-0089-5}

\leavevmode\hypertarget{ref-brown2017}{}%
Brown, N. J. L., \& Heathers, J. A. J. (2017). The GRIM Test: A Simple Technique Detects Numerous Anomalies in the Reporting of Results in Psychology. \emph{Social Psychological and Personality Science}, \emph{8}(4), 363--369. \url{https://doi.org/10.1177/1948550616673876}

\leavevmode\hypertarget{ref-cohen1962}{}%
Cohen, J. (1962). The statistical power of abnormal-social psychological research: a review. \emph{Journal of Abnormal and Social Psychology}, \emph{65}, 145--153. \url{https://doi.org/10.1037/h0045186}

\leavevmode\hypertarget{ref-cohen1988}{}%
Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). New York: Routledge. \url{https://doi.org/10.4324/9780203771587}

\leavevmode\hypertarget{ref-correll2020}{}%
Correll, J., Mellinger, C., McClelland, G. H., \& Judd, C. M. (2020). Avoid cohen{'}s {`}small{'}, {`}medium{'}, and {`}large{'} for power analysis. \emph{Trends in Cognitive Sciences}, \emph{24}(3), 200--207. \url{https://doi.org/10.1016/j.tics.2019.12.009}

\leavevmode\hypertarget{ref-R-lemon}{}%
Edwards, S. M. (2020). \emph{Lemon: Freshing up your 'ggplot2' plots}. Retrieved from \url{https://CRAN.R-project.org/package=lemon}

\leavevmode\hypertarget{ref-field2016}{}%
Field, A. P. (2016). \emph{An adventure in statistics: The reality enigma}.

\leavevmode\hypertarget{ref-fischman2015}{}%
Fischman, M. G. (2015). On the continuing problem of inappropriate learning measures: Comment on Wulf et al. (2014) and Wulf et al. (2015). \emph{Human Movement Science}, \emph{42}, 225--231. \url{https://doi.org/10.1016/j.humov.2015.05.011}

\leavevmode\hypertarget{ref-R-daff}{}%
Fitzpatrick, P., de Jonge, E., \& Warnes, G. R. (2019). \emph{Daff: Diff, patch and merge for data.frames}. Retrieved from \url{https://CRAN.R-project.org/package=daff}

\leavevmode\hypertarget{ref-gray2021}{}%
Gray, R. {[}@ShakeyWaits{]}. (2021). \emph{The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress}. {[}Tweet; Thumbnail link to article{]}. Twitter. \url{https://twitter.com/ShakeyWaits/status/1359501377073012736}.

\leavevmode\hypertarget{ref-hancock1995}{}%
Hancock, G. R., Butler, M. S., \& Fischman, M. G. (1995). On the problem of two-dimensional error scores: Measures and analyses of accuracy, bias, and consistency. \emph{Journal of Motor Behavior}, \emph{27}(3), 241--250. \url{https://doi.org/10.1080/00222895.1995.9941714}

\leavevmode\hypertarget{ref-lakens2013}{}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}. \url{https://doi.org/10.3389/fpsyg.2013.00863}

\leavevmode\hypertarget{ref-lola2020}{}%
Lola, A. C., \& Tzetzis, G. C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. \emph{Journal of Physical Education and Sport}, \emph{20}(5), 2478--2486. Retrieved from \url{https://www.cabdirect.org/cabdirect/abstract/20203562097}

\leavevmode\hypertarget{ref-lola2021}{}%
Lola, A. C., \& Tzetzis, G. C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. \emph{International Journal of Sport and Exercise Psychology}, \emph{0}(0), 1--21. \url{https://doi.org/10.1080/1612197X.2021.1877325}

\leavevmode\hypertarget{ref-lola2012}{}%
Lola, A. C., Tzetzis, G. C., \& Zetou, H. (2012). The Effect of Implicit and Explicit Practice in the Development of Decision Making in Volleyball Serving. \emph{Perceptual and Motor Skills}, \emph{114}(2), 665--678. \url{https://doi.org/10.2466/05.23.25.PMS.114.2.665-678}

\leavevmode\hypertarget{ref-lovakov2021}{}%
Lovakov, A., \& Agadullina, E. R. (2021). Empirically derived guidelines for effect size interpretation in social psychology. \emph{European Journal of Social Psychology}, \emph{00}, 1--20. \url{https://doi.org/10.1002/ejsp.2752}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man, donotrepeattitle,floatsintext]{apa7}
\title{Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)}
\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Data irregularities across five implicit learning articles: Comments on Lola, Tzetzis, and Zetou (2012); Lola and Tzetzis (2020); Lola and Tzetzis (2021); Tzetzis and Lola (2010); Tzetzis and Lola (2015)},
  pdfauthor={Brad McKay1 \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Meta-science; GRIMMER; Effect sizes; Perceptual motor learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{xcolor}
\raggedbottom
\pagewiselinenumbers
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

We reanalyzed five articles by Afroditi Lola, George Tzetzis, and their colleague (Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015). All five papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. We will refer to the five articles throughout this paper using the following numbering system:

@@

The primary outcome measures used in these experiments were reaction time (Articles 1, 3, 4, and 5), response accuracy (Articles 1, 3, 4), and motor performance measured on a 4-point scale (Article 2). In addition, Articles 1 and 5 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 2 had a measure of self-efficacy using a Likert scale. Articles 1, 3, 4, and 5 also analyzed the number of explicit rules recalled.

@@

None of the five articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 2-5 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 2-5. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication about our concerns regarding the data irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns. Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles. The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data \emph{and} analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: \url{https://osf.io/raz6q/}.

@@

To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in Articles 1-5, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}). We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation. The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97. In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature. The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.

@@

\caption{Absolute Cohen's \(d\) estimates from Articles 1-4 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of \(d\) = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
\end{figure}

@@

Eta-squared (\(\eta^{2}\)) is calculated by dividing the sum of squares for the effect by the total sum of squares. It can be interpreted as analogous to \(R^{2}\) as it represents the total variation in the dependent measure that can be explained by a given main effect or interaction in an ANOVA (Lakens, 2013). Benchmarks have been suggested for small, medium, and large effect sizes as \(\eta^{2}\) = .01, .06, and .14, respectively (Cohen, 1988). Importantly, if a main effect of instruction-type results in \(\eta^{2}\) = .99, as was commonly reported in the target articles, this suggests that 99\% of the total variability in the outcome measure can be explained by group assignment alone. Such a result is implausible.

@@

We have reviewed concerning data irregularities spanning five articles investigating implicit motor and perceptual learning (Lola \& Tzetzis, 2020, 2021; Lola et al., 2012; Tzetzis \& Lola, 2010, 2015). These data irregularities include implausibly large effect sizes for pairwise comparisons and impossible descriptive statistics---both of which have been acknowledged by the authors as misprints due to an outsourcing of table formatting (A. Lola, personal communication, April 22, 2021). Further, the reported test statistics and associated \(\eta^{2}\) values are also implausibly large, which is inconsistent with the authors' claim that the results and discussions remain valid despite these aforementioned typographic errors in the tables. Considering these findings, the conclusions from these articles are not reliable.

It is noteworthy that the results reported in each of these articles perfectly reflect the authors' expectations. Indeed, our attention was drawn to these articles after the Lola and Tzetzis (2021) paper was shared on Twitter (Gray, 2021); possibly because the results appeared to be exemplary. Although these errors seem unlikely to have aligned with expectations by chance alone, our exposure to them occurred after they had been selected for publication. We cannot rule out that these papers were selected for publication because of exemplary results and happened to have errors, and this selection caused those errors to correlate with the authors' expectations.

Other irregularities, such as a repeating \emph{F}-statistic for all four analyses of explicit rules and the recurring age of participants, potentially reflect sloppiness more than expectation. Indeed, the authors have already admitted that some values reported in their tables were in error, and it seems errors occurred in each of the articles we have reviewed. These errors were pervasive and appear to have substantially affected the conclusions of the articles in question. At a minimum, the consistent reporting errors across these five articles seem to reflect excessive carelessness throughout the publication process. Even if the authors offer corrections, which they have suggested they intend to do\footnote{As of today's date (2021-09-11), there is no indication that such corrective actions have been taken by the authors.}, many in the research community may find it difficult to trust any of these results.

@@

\label{sec:sharing} All material, data, and scripts to reproduce our analyses and figure can be accessed here: \url{https://osf.io/raz6q/}.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-anaya2016}{}}%
Anaya, J. (2016). \emph{The GRIMMER test: A method for testing the validity of reported measures of variability}. \url{https://doi.org/10.7287/peerj.preprints.2400v1}

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-bakker2011}{}}%
Bakker, M., \& Wicherts, J. M. (2011). The (mis)reporting of statistical results in psychology journals. \emph{Behavior Research Methods}, \emph{43}(3), 666--678. \url{https://doi.org/10.3758/s13428-011-0089-5}

\leavevmode\vadjust pre{\hypertarget{ref-brown2017}{}}%
Brown, N. J. L., \& Heathers, J. A. J. (2017). The GRIM Test: A Simple Technique Detects Numerous Anomalies in the Reporting of Results in Psychology. \emph{Social Psychological and Personality Science}, \emph{8}(4), 363--369. \url{https://doi.org/10.1177/1948550616673876}

\leavevmode\vadjust pre{\hypertarget{ref-cohen1962}{}}%
Cohen, J. (1962). The statistical power of abnormal-social psychological research: a review. \emph{Journal of Abnormal and Social Psychology}, \emph{65}, 145--153. \url{https://doi.org/10.1037/h0045186}

\leavevmode\vadjust pre{\hypertarget{ref-cohen1988}{}}%
Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). New York: Routledge. \url{https://doi.org/10.4324/9780203771587}

\leavevmode\vadjust pre{\hypertarget{ref-correll2020}{}}%
Correll, J., Mellinger, C., McClelland, G. H., \& Judd, C. M. (2020). Avoid cohen{'}s {`}small{'}, {`}medium{'}, and {`}large{'} for power analysis. \emph{Trends in Cognitive Sciences}, \emph{24}(3), 200--207. \url{https://doi.org/10.1016/j.tics.2019.12.009}

\leavevmode\vadjust pre{\hypertarget{ref-R-lemon}{}}%
Edwards, S. M. (2020). \emph{Lemon: Freshing up your 'ggplot2' plots}. Retrieved from \url{https://CRAN.R-project.org/package=lemon}

\leavevmode\vadjust pre{\hypertarget{ref-field2016}{}}%
Field, A. P. (2016). \emph{An adventure in statistics: The reality enigma}.

\leavevmode\vadjust pre{\hypertarget{ref-fischman2015}{}}%
Fischman, M. G. (2015). On the continuing problem of inappropriate learning measures: Comment on Wulf et al. (2014) and Wulf et al. (2015). \emph{Human Movement Science}, \emph{42}, 225--231. \url{https://doi.org/10.1016/j.humov.2015.05.011}

\leavevmode\vadjust pre{\hypertarget{ref-R-daff}{}}%
Fitzpatrick, P., de Jonge, E., \& Warnes, G. R. (2019). \emph{Daff: Diff, patch and merge for data.frames}. Retrieved from \url{https://CRAN.R-project.org/package=daff}

\leavevmode\vadjust pre{\hypertarget{ref-gray2021}{}}%
Gray, R. {[}@ShakeyWaits{]}. (2021). \emph{The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress}. {[}Tweet; Thumbnail link to article{]}. Twitter. \url{https://twitter.com/ShakeyWaits/status/1359501377073012736}.

\leavevmode\vadjust pre{\hypertarget{ref-hancock1995}{}}%
Hancock, G. R., Butler, M. S., \& Fischman, M. G. (1995). On the problem of two-dimensional error scores: Measures and analyses of accuracy, bias, and consistency. \emph{Journal of Motor Behavior}, \emph{27}(3), 241--250. \url{https://doi.org/10.1080/00222895.1995.9941714}

\leavevmode\vadjust pre{\hypertarget{ref-lakens2013}{}}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}. \url{https://doi.org/10.3389/fpsyg.2013.00863}

\leavevmode\vadjust pre{\hypertarget{ref-lola2020}{}}%
Lola, A. C., \& Tzetzis, G. C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. \emph{Journal of Physical Education and Sport}, \emph{20}(5), 2478--2486. Retrieved from \url{https://www.cabdirect.org/cabdirect/abstract/20203562097}

\leavevmode\vadjust pre{\hypertarget{ref-lola2021}{}}%
Lola, A. C., \& Tzetzis, G. C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. \emph{International Journal of Sport and Exercise Psychology}, \emph{0}(0), 1--21. \url{https://doi.org/10.1080/1612197X.2021.1877325}

\leavevmode\vadjust pre{\hypertarget{ref-lola2012}{}}%
Lola, A. C., Tzetzis, G. C., \& Zetou, H. (2012). The Effect of Implicit and Explicit Practice in the Development of Decision Making in Volleyball Serving. \emph{Perceptual and Motor Skills}, \emph{114}(2), 665--678. \url{https://doi.org/10.2466/05.23.25.PMS.114.2.665-678}

\leavevmode\vadjust pre{\hypertarget{ref-lovakov2021}{}}%
Lovakov, A., \& Agadullina, E. R. (2021). Empirically derived guidelines for effect size interpretation in social psychology. \emph{European Journal of Social Psychology}, \emph{00}, 1--20. \url{https://doi.org/10.1002/ejsp.2752}
